The hedging hyperprior for the exponential distribution

### 2023-03-07 text/23/exponential-hedging-hyperprior.Rmd
Converted to correct name for exponential-hedging-hyperprior

I want to write a paper about the hedging hyperprior. I need to work out some simple examples first. Here is an example involving the gamma distribution.

@@

Consider a Bayesian analysis of an outcome variable that has an exponential distribution. The density of the gamma distribution is

@@

```{r}
g_grid <- g(x_grid, a0, b0)
sum(g_grid)*0.01 # Check the g is a density.
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```

>>>>

I want to write a paper about the hedging hyperprior. I need to work out some simple examples first. Here is an example involving the exponential distribution.

@@

Consider a Bayesian analysis of an outcome variable that has an exponential distribution. The density of the exponential distribution is

@@

```{r}
g_grid <- g(x_grid, a0, b0)
outside <- x_grid < prior05 | x_grid > prior95
x_color <- 
  ifelse(outside, "white", "gray")
data.frame(x=x_grid, y=g_grid) %>%
  ggplot(aes(x, y)) +
    geom_segment(aes(xend=x, yend=0), color=x_color) +
    geom_line() + xlab(" ") + ylab(" ")
```
